Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/content/revisited.tex
actually let me bold this

\begin{finding}
\textit{For sufficiently low warm start \emph{under the instances that are relative reputation costly}, the optimal strategies in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $DG$ \\
\textbf{Temporary Monopoly} - $\TS$ \\
\textbf{Permanent Duopoly} - $DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}

>>>>

\begin{finding}
\textit{For sufficiently low warm start \textbf{under the instances that are relative reputation costly}, the optimal strategies in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $DG$ \\
\textbf{Temporary Monopoly} - $\TS$ \\
\textbf{Permanent Duopoly} - $DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}
